Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-10-15 ijgi-148112-for proofreading/ijgi-148112-can be published.tex
new author list

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,3}$ and Zhenhong Du $^{2,3,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{2}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn\\
$^{3}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}

@@

\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
  Ma]{zheng2008understanding}
Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
\newblock Understanding mobility based on GPS data.
\newblock  In Proceedings of the 10th International Conference on Ubiquitous
  Computing, Seoul, South Korea, 21--24 September 2008.

\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
Jiang, B.; Yin, J.; Zhao, S.
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Phys. Rev. E} {\bf 2009}, doi:10.1103/PhysRevE.80.021136.

\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
Belik, V.; Geisel, T.; Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Phys. Rev. X} {\bf 2011}, doi:10.1103/PhysRevX.1.011001.

\bibitem[Greenwood(1985)]{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em J. Reg. Sci.} {\bf 1985}, {\em 25},~521--544.

@@

\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
  Newth]{Jurdak2015}
Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
\newblock Understanding human mobility from twitter.
\newblock {\em PLoS One} {\bf 2015}, doi:10.1371/journal.pone.0131469.

\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
  Chong]{rhee2011levy}
Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM Trans. Netw.} {\bf 2011}, {\em
  19},~630--643.

\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
Sevtsuk, A.; Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em J. Urban Technol.} {\bf 2010}, {\em 17},~41--60.

\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
  Ratti]{kung2014exploring}
Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS One} {\bf 2014}, doi:10.1371/journal.pone.0096180.

\bibitem[Thatcher(2014)]{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em Int. J. Commun.} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
  Kazakopoulos, and Ratti]{hawelka2014geo}
Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2014}, {\em
  41},~260--271.

\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
Giannotti, F.; Pedreschi, D.
\newblock {\em Mobility, Data Mining and Privacy: Geographic Knowledge
  Discovery}; Springer Science \& Business Media: Berlin, Germany,  2008.

\bibitem[Crampton(2014)]{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: National security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, {\em 9}, 1--13.

\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PLoS one} {\bf 2014}, doi:10.1371/journal.pone.0097010.

\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
  Ukkusuri]{hasan2013understanding}
Hasan, S.; Zhan, X.; Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  In Proceedings of the 2nd ACM SIGKDD International Workshop on Urban
  Computing, Chicago, IL, USA, 11--14 August 2013.

\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
Cho, E.; Myers, S.A.; Leskovec, J.
\newblock Friendship and mobility: User movement in location-based social
  networks.
\newblock  In Proceedings of the 17th ACM SIGKDD International Conference on
  Knowledge Discovery and Data Mining, San Diego, CA, USA, 21--24 August 2011.

\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
  Mascolo]{noulas2012tale}
Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
\newblock A tale of many cities: Universal patterns in human urban mobility.
\newblock {\em PLoS One} {\bf 2012}, doi:10.1371/journal.pone.0037027.

\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
  and Vespignani]{balcan2009multiscale}
Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proc. Nat. Acad. Sci.} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
  Alonso]{tamerius2011global}
Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
\newblock Global influenza seasonality: Reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environ. Health Perspect.} {\bf 2011}, {\em 119},~439--445.

\bibitem[Tsou(2015)]{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2015}, {\em
  42},~70--74.

\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
Zheng, Y.; Xie, X.; Ma, W.Y.
\newblock GeoLife: A collaborative social networking service among user,
  location and trajectory. {\em IEEE Data(base) Eng. Bulletin} {\bf 2010}, {\em 33}, 32--39.

\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Commun. ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
  Smoreda, and Ratti]{sobolevsky2013delineating}
Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0081707.

\bibitem[Twitter (2016)]{twitterAPI}
Twitter Streaming API
\newblock available from: https://dev.twitter.com/streaming/overview
\newblock {\bf 2016}, accessed on October, 2016

\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
  Sadeh]{cranshaw2012livehoods}
Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
\newblock The livehoods project: Utilizing social media to understand the
  dynamics of a city.
\newblock  In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.

\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
  Danforth]{mitchell2013geography}
Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place. {\em PLoS One} {\bf 2013}, doi:10.1371/journal.pone.0064417.

\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
  et~al.]{longley2015geotemporal}
Longley, P.A.; Adnan, M.; Lansley, G.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environ. Plan. A} {\bf 2015}, {\em 47},~465--484.

\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
  et~al.]{hagerstrand1985time}
H{\"a}gerstrand, T.
\newblock Time-geography: Focus on the corporeality of man, society, and
  environment.
\newblock In {\em The Science and Praxis of Complexity}; United Nations University: Montpellier, France, 1985; pp. 193--216.

\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
Kwan, M.P.; Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: A
  time-geographic approach. In 
\newblock {\em Spatially Integrated Social Science: Examples in Best Practice}; Michael, F.G., Donald, G.J. Eds.; Oxford University Press: Oxford, MI, USA, 2003; Volume 3, pp. 27--51.

\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
Andrienko, N.; Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartogr. Int. J. Geogr.
  Inf. Geovis.} {\bf 2007}, {\em 42},~117--138.

\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
MacEachren, A.M.; Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartogr. Geogr. Inf. Sci.} {\bf 2001}, {\em
  28},~3--12.

\bibitem[MacEachren(2004)]{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How Maps Work: Representation, Visualization, and Design};
  Guilford Press: New York, NY, USA, 2004.

\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
  Wrobel]{andrienko2007visual}
Andrienko, G.; Andrienko, N.; Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explor. Newsl.} {\bf 2007}, {\em 9},~38--46.

\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
  Soltani]{cao2014scalable}
Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
\newblock A scalable framework for spatiotemporal analysis of location-based
  social media data.
\newblock {\em Comput. Environ. Urban Syst.} {\bf 2015}, {\em 51}, 70--82.

\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
  Liu, Y.
\newblock FluMapper: A cyberGIS application for interactive analysis of massive
  location-based social media.
\newblock {\em Concurr. Comput. Pract. Exp.} {\bf
  2014}, doi:10.1002/cpe.3287.

\bibitem[Black \em{et~al.}(2012)Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.]{black2012twitter}
Black, A., Mascaro, C., Gallagher, M. and Goggins, S.P.
\newblock DTwitter zombie: Architecture for capturing, socially transforming and analyzing the Twittersphere
\newblock In {\em Proceedings of the 17th ACM international conference on Supporting group work} {\bf 2012}, pp. 229-238. ACM.

\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
  Chansler]{shvachko2010hadoop}
Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
\newblock The hadoop distributed file system.
\newblock  {\em Mass Storage Syst. Technol.}  {\bf 2010}, doi:10.1109/MSST.2010.5496972.

\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
Dean, J.; Ghemawat, S.
\newblock MapReduce: Simplified data processing on large clusters.
\newblock {\em Commun. ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
Gao, H.; Tang, J.; Liu, H.
\newblock Exploring social-historical ties on location-based social networks.
\newblock In Proceedings of the ICWSM 2012, Dublin, Ireland, 4--8 June 2012.

\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
Buttenfield, B.P.; McMaster, R.B.
\newblock {\em Map Generalization: Making Rules for Knowledge Representation};
  Longman Scientific \& Technical: New York, NY, USA, 1991.

\bibitem[Samet(1984)]{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Comput. Surv. (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
  Newman]{clauset2009power}
Clauset, A.; Shalizi, C.R.; Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM Rev.} {\bf 2009}, {\em 51},~661--703.

\bibitem[Reynolds(2012)]{reynolds2012truncated}
Reynolds, A.
\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
  collection when correlated random walks embody observed movement patterns.
\newblock {\em J. Royal Soc. Int.} {\bf 2012}, {\em
  9},~528--534.

\bibitem[Zhao \em{et~al.}(2015)Zhao, Musolesi, Hui, Rao, and
  Tarkoma]{zhao2015explaining}
Zhao, K.; Musolesi, M.; Hui, P.; Rao, W.; Tarkoma, S.
\newblock Explaining the power-law distribution of human mobility through
  transportation modality decomposition.
\newblock {\em Sci. Rep.} {\bf 2015}, doi:10.1038/srep09136.

\bibitem[Liu \em{et~al.}(2014)Liu, Padmanabhan, and Wang]{liu2014cybergis}
Liu, Y.; Padmanabhan, A.; Wang, S.
\newblock CyberGIS Gateway for enabling data-rich geospatial research and
  education.
\newblock {\em Sci. Gatew. Workshops 2013} {\bf
  2014}, doi:10.1002/cpe.3256.

>>>>

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,2}$, Shaowen Wang $^{1,2,3}$ and Zhenhong Du $^{4,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin, Shaowen Wang and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
$^{2}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Shaowen Wang conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Shaowen Wang and Zhenhong Du wrote the paper.}

@@

\bibitem[Zheng \em{et~al.}(2008)Zheng, Li, Chen, Xie, and
  Ma]{zheng2008understanding}
Zheng, Y.; Li, Q.; Chen, Y.; Xie, X.; Ma, W.Y.
\newblock Understanding mobility based on GPS data.
\newblock  Proceedings of the 10th international conference on Ubiquitous
  computing. ACM,  2008, pp. 312--321.

\bibitem[Jiang \em{et~al.}(2009)Jiang, Yin, and Zhao]{jiang2009characterizing}
Jiang, B.; Yin, J.; Zhao, S.
\newblock Characterizing the human mobility pattern in a large street network.
\newblock {\em Physical Review E} {\bf 2009}, {\em 80},~021136.

\bibitem[Belik \em{et~al.}(2011)Belik, Geisel, and Brockmann]{belik2011natural}
Belik, V.; Geisel, T.; Brockmann, D.
\newblock Natural human mobility patterns and spatial spread of infectious
  diseases.
\newblock {\em Physical Review X} {\bf 2011}, {\em 1},~011001.

\bibitem[Greenwood(1985)]{greenwood1985human}
Greenwood, M.J.
\newblock Human migration: Theory, models, and empirical studies.
\newblock {\em Journal of regional Science} {\bf 1985}, {\em 25},~521--544.

@@

\bibitem[Jurdak \em{et~al.}(2015)Jurdak, Zhao, Liu, AbouJaoude, Cameron, and
  Newth]{Jurdak2015}
Jurdak, R.; Zhao, K.; Liu, J.; AbouJaoude, M.; Cameron, M.; Newth, D.
\newblock Understanding Human Mobility from Twitter.
\newblock {\em PLoS ONE} {\bf 2015}, {\em 10},~e0131469.

\bibitem[Rhee \em{et~al.}(2011)Rhee, Shin, Hong, Lee, Kim, and
  Chong]{rhee2011levy}
Rhee, I.; Shin, M.; Hong, S.; Lee, K.; Kim, S.J.; Chong, S.
\newblock On the levy-walk nature of human mobility.
\newblock {\em IEEE/ACM transactions on networking (TON)} {\bf 2011}, {\em
  19},~630--643.

\bibitem[Sevtsuk and Ratti(2010)]{sevtsuk2010does}
Sevtsuk, A.; Ratti, C.
\newblock Does urban mobility have a daily routine? Learning from the aggregate
  data of mobile networks.
\newblock {\em Journal of Urban Technology} {\bf 2010}, {\em 17},~41--60.

\bibitem[Kung \em{et~al.}(2014)Kung, Greco, Sobolevsky, and
  Ratti]{kung2014exploring}
Kung, K.S.; Greco, K.; Sobolevsky, S.; Ratti, C.
\newblock Exploring universal patterns in human home-work commuting from mobile
  phone data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e96180.

\bibitem[Thatcher(2014)]{thatcher2014living}
Thatcher, J.
\newblock Living on fumes: Digital footprints, data fumes, and the limitations
  of spatial big data.
\newblock {\em International Journal of Communication} {\bf 2014}, {\em
  8},~1765--1783.

\bibitem[Hawelka \em{et~al.}(2014)Hawelka, Sitko, Beinat, Sobolevsky,
  Kazakopoulos, and Ratti]{hawelka2014geo}
Hawelka, B.; Sitko, I.; Beinat, E.; Sobolevsky, S.; Kazakopoulos, P.; Ratti, C.
\newblock Geo-located Twitter as proxy for global mobility patterns.
\newblock {\em Cartography and Geographic Information Science} {\bf 2014}, {\em
  41},~260--271.

\bibitem[Giannotti and Pedreschi(2008)]{giannotti2008mobility}
Giannotti, F.; Pedreschi, D.
\newblock {\em Mobility, data mining and privacy: Geographic knowledge
  discovery}; Springer Science \& Business Media,  2008.

\bibitem[Crampton(2014)]{crampton2014collect}
Crampton, J.W.
\newblock Collect it all: national security, Big Data and governance.
\newblock {\em GeoJournal} {\bf 2014}, pp. 1--13.

\bibitem[Wu \em{et~al.}(2014)Wu, Zhi, Sui, and Liu]{wu2014intra}
Wu, L.; Zhi, Y.; Sui, Z.; Liu, Y.
\newblock Intra-urban human mobility and activity transition: Evidence from
  social media check-in data.
\newblock {\em PloS one} {\bf 2014}, {\em 9},~e97010.

\bibitem[Hasan \em{et~al.}(2013)Hasan, Zhan, and
  Ukkusuri]{hasan2013understanding}
Hasan, S.; Zhan, X.; Ukkusuri, S.V.
\newblock Understanding urban human activity and mobility patterns using
  large-scale location-based data from online social media.
\newblock  Proceedings of the 2nd ACM SIGKDD international workshop on urban
  computing. ACM,  2013, p.~6.

\bibitem[Cho \em{et~al.}(2011)Cho, Myers, and Leskovec]{cho2011friendship}
Cho, E.; Myers, S.A.; Leskovec, J.
\newblock Friendship and mobility: user movement in location-based social
  networks.
\newblock  Proceedings of the 17th ACM SIGKDD international conference on
  Knowledge discovery and data mining. ACM,  2011, pp. 1082--1090.

\bibitem[Noulas \em{et~al.}(2012)Noulas, Scellato, Lambiotte, Pontil, and
  Mascolo]{noulas2012tale}
Noulas, A.; Scellato, S.; Lambiotte, R.; Pontil, M.; Mascolo, C.
\newblock A tale of many cities: universal patterns in human urban mobility.
\newblock {\em PloS one} {\bf 2012}, {\em 7},~e37027.

\bibitem[Balcan \em{et~al.}(2009)Balcan, Colizza, Gon{\c{c}}alves, Hu, Ramasco,
  and Vespignani]{balcan2009multiscale}
Balcan, D.; Colizza, V.; Gon{\c{c}}alves, B.; Hu, H.; Ramasco, J.J.;
  Vespignani, A.
\newblock Multiscale mobility networks and the spatial spreading of infectious
  diseases.
\newblock {\em Proceedings of the National Academy of Sciences} {\bf 2009},
  {\em 106},~21484--21489.

\bibitem[Tamerius \em{et~al.}(2011)Tamerius, Nelson, Zhou, Viboud, Miller, and
  Alonso]{tamerius2011global}
Tamerius, J.; Nelson, M.I.; Zhou, S.Z.; Viboud, C.; Miller, M.A.; Alonso, W.J.
\newblock Global influenza seasonality: reconciling patterns across temperate
  and tropical regions.
\newblock {\em Environmental health perspectives} {\bf 2011}, {\em 119},~439.

\bibitem[Tsou(2015)]{tsou2015}
Tsou, M.H.
\newblock Research challenges and opportunities in mapping social media and Big
  Data.
\newblock {\em Cartography and Geographic Information Science} {\bf 2015}, {\em
  42},~70--74.

\bibitem[Zheng \em{et~al.}(2010)Zheng, Xie, and Ma]{zheng2010geolife}
Zheng, Y.; Xie, X.; Ma, W.Y.
\newblock GeoLife: A Collaborative Social Networking Service among User,
  Location and Trajectory. {\bf 2010}.

\bibitem[Becker \em{et~al.}(2013)Becker, C{\'a}ceres, Hanson, Isaacman, Loh,
  Martonosi, Rowland, Urbanek, Varshavsky, and Volinsky]{becker2013human}
Becker, R.; C{\'a}ceres, R.; Hanson, K.; Isaacman, S.; Loh, J.M.; Martonosi,
  M.; Rowland, J.; Urbanek, S.; Varshavsky, A.; Volinsky, C.
\newblock Human mobility characterization from cellular network data.
\newblock {\em Communications of the ACM} {\bf 2013}, {\em 56},~74--82.

\bibitem[Sobolevsky \em{et~al.}(2013)Sobolevsky, Szell, Campari, Couronn{\'e},
  Smoreda, and Ratti]{sobolevsky2013delineating}
Sobolevsky, S.; Szell, M.; Campari, R.; Couronn{\'e}, T.; Smoreda, Z.; Ratti,
  C.
\newblock Delineating geographical regions with networks of human interactions
  in an extensive set of countries.
\newblock {\em PLoS One} {\bf 2013}, {\em 8},~e81707.

\bibitem[Twitter(2016)]{twitterAPI}
Twitter.
\newblock Twitter streaming API.
\newblock {\em available from: https://dev.twitter.com/streaming/overview} {\bf
  2016}.

\bibitem[Cranshaw \em{et~al.}(2012)Cranshaw, Schwartz, Hong, and
  Sadeh]{cranshaw2012livehoods}
Cranshaw, J.; Schwartz, R.; Hong, J.I.; Sadeh, N.M.
\newblock The Livehoods Project: Utilizing Social Media to Understand the
  Dynamics of a City.
\newblock  ICWSM,  2012.

\bibitem[Mitchell \em{et~al.}(2013)Mitchell, Frank, Harris, Dodds, and
  Danforth]{mitchell2013geography}
Mitchell, L.; Frank, M.R.; Harris, K.D.; Dodds, P.S.; Danforth, C.M.
\newblock The geography of happiness: Connecting twitter sentiment and
  expression, demographics, and objective characteristics of place {\bf 2013}.

\bibitem[Longley \em{et~al.}(2015)Longley, Adnan, Lansley,
  et~al.]{longley2015geotemporal}
Longley, P.A.; Adnan, M.; Lansley, G.; others.
\newblock The geotemporal demographics of Twitter usage.
\newblock {\em Environment and Planning A} {\bf 2015}, {\em 47},~465--484.

\bibitem[H{\"a}gerstrand \em{et~al.}(1985)H{\"a}gerstrand
  et~al.]{hagerstrand1985time}
H{\"a}gerstrand, T.; others.
\newblock Time-geography: focus on the corporeality of man, society, and
  environment.
\newblock {\em The science and praxis of complexity} {\bf 1985}, pp. 193--216.

\bibitem[Kwan and Lee(2004)]{kwan2004geovisualization}
Kwan, M.P.; Lee, J.
\newblock Geovisualization of human activity patterns using 3D GIS: a
  time-geographic approach.
\newblock {\em Spatially integrated social science} {\bf 2004}, {\em 27}.

\bibitem[Andrienko and Andrienko(2007)]{andrienko2007designing}
Andrienko, N.; Andrienko, G.
\newblock Designing visual analytics methods for massive collections of
  movement data.
\newblock {\em Cartographica: The International Journal for Geographic
  Information and Geovisualization} {\bf 2007}, {\em 42},~117--138.

\bibitem[MacEachren and Kraak(2001)]{maceachren2001research}
MacEachren, A.M.; Kraak, M.J.
\newblock Research challenges in geovisualization.
\newblock {\em Cartography and Geographic Information Science} {\bf 2001}, {\em
  28},~3--12.

\bibitem[MacEachren(2004)]{maceachren2004maps}
MacEachren, A.M.
\newblock {\em How maps work: representation, visualization, and design};
  Guilford Press,  2004.

\bibitem[Andrienko \em{et~al.}(2007)Andrienko, Andrienko, and
  Wrobel]{andrienko2007visual}
Andrienko, G.; Andrienko, N.; Wrobel, S.
\newblock Visual analytics tools for analysis of movement data.
\newblock {\em ACM SIGKDD Explorations Newsletter} {\bf 2007}, {\em 9},~38--46.

\bibitem[Cao \em{et~al.}(2015)Cao, Wang, Hwang, Padmanabhan, Zhang, and
  Soltani]{cao2014scalable}
Cao, G.; Wang, S.; Hwang, M.; Padmanabhan, A.; Zhang, Z.; Soltani, K.
\newblock A scalable framework for spatiotemporal analysis of location-based
  social media data.
\newblock {\em Computers, Environment and Urban Systems} {\bf 2015}, {\em
  51},~70--82.

\bibitem[Padmanabhan \em{et~al.}(2014)Padmanabhan, Wang, Cao, Hwang, Zhang,
  Gao, Soltani, and Liu]{padmanabhan2014flumapper}
Padmanabhan, A.; Wang, S.; Cao, G.; Hwang, M.; Zhang, Z.; Gao, Y.; Soltani, K.;
  Liu, Y.
\newblock FluMapper: A cyberGIS application for interactive analysis of massive
  location-based social media.
\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
  2014}.

\bibitem[Black \em{et~al.}(2012)Black, Mascaro, Gallagher, and
  Goggins]{black2012twitter}
Black, A.; Mascaro, C.; Gallagher, M.; Goggins, S.P.
\newblock Twitter zombie: Architecture for capturing, socially transforming and
  analyzing the Twittersphere.
\newblock  Proceedings of the 17th ACM international conference on Supporting
  group work. ACM,  2012, pp. 229--238.

\bibitem[Shvachko \em{et~al.}(2010)Shvachko, Kuang, Radia, and
  Chansler]{shvachko2010hadoop}
Shvachko, K.; Kuang, H.; Radia, S.; Chansler, R.
\newblock The hadoop distributed file system.
\newblock  Mass Storage Systems and Technologies (MSST), 2010 IEEE 26th
  Symposium on. IEEE,  2010, pp. 1--10.

\bibitem[Dean and Ghemawat(2008)]{dean2008mapreduce}
Dean, J.; Ghemawat, S.
\newblock MapReduce: simplified data processing on large clusters.
\newblock {\em Communications of the ACM} {\bf 2008}, {\em 51},~107--113.

\bibitem[Gao \em{et~al.}(2012)Gao, Tang, and Liu]{gao2012exploring}
Gao, H.; Tang, J.; Liu, H.
\newblock Exploring Social-Historical Ties on Location-Based Social Networks.
\newblock  ICWSM,  2012.

\bibitem[Buttenfield and McMaster(1991)]{buttenfield1991map}
Buttenfield, B.P.; McMaster, R.B.
\newblock {\em Map Generalization: Making rules for knowledge representation};
  Longman Scientific \& Technical New York,  1991.

\bibitem[Samet(1984)]{samet1984quadtree}
Samet, H.
\newblock The quadtree and related hierarchical data structures.
\newblock {\em ACM Computing Surveys (CSUR)} {\bf 1984}, {\em 16},~187--260.

\bibitem[Clauset \em{et~al.}(2009)Clauset, Shalizi, and
  Newman]{clauset2009power}
Clauset, A.; Shalizi, C.R.; Newman, M.E.
\newblock Power-law distributions in empirical data.
\newblock {\em SIAM review} {\bf 2009}, {\em 51},~661--703.

\bibitem[Reynolds(2012)]{reynolds2012truncated}
Reynolds, A.
\newblock Truncated L{\'e}vy walks are expected beyond the scale of data
  collection when correlated random walks embody observed movement patterns.
\newblock {\em Journal of The Royal Society Interface} {\bf 2012}, {\em
  9},~528--534.

\bibitem[Zhao \em{et~al.}(2015)Zhao, Musolesi, Hui, Rao, and
  Tarkoma]{zhao2015explaining}
Zhao, K.; Musolesi, M.; Hui, P.; Rao, W.; Tarkoma, S.
\newblock Explaining the power-law distribution of human mobility through
  transportation modality decomposition.
\newblock {\em Scientific reports} {\bf 2015}, {\em 5}.

\bibitem[Liu \em{et~al.}(2014)Liu, Padmanabhan, and Wang]{liu2014cybergis}
Liu, Y.; Padmanabhan, A.; Wang, S.
\newblock CyberGIS Gateway for enabling data-rich geospatial research and
  education.
\newblock {\em Concurrency and Computation: Practice and Experience} {\bf
  2014}.
